Multimatrices and Their Derivatives

### 2019-05-10 Math/paper.tex
Some more progress on the math.

\DeclareMathOperator{\Dim}{Dim}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

Which isn't a huge improvement over our original notation. What would be great is
if we could define the total derivative without going down into the partial derivatives
at all, which we'll be able to do in later sections. As a sneak peak, that'll look
like this:
\[
\frac{dM}{dX} = I^3(|X|) \mmult{||X||} \cos(X)
\]

But that single line will require defining something I'm going to call a cubic
identity, $I^3(|X|)$, as well as multimatrix multiplication.

@@

\begin{definition}[Multimatrix Multiplication]
\label{mm_mult}
Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$,
$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$.
Then $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$ and
\[
\forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}):
(A \mmult{n}  B)[\bar{a} \oplus \bar{b}] =
\sum_{\forall \bar{c} \in \Dim(\vec{c})}
  A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
\]
\end{definition}

Like two dimensional matrix multiplication, multimatrix multiplication is
\textit{not} communicative. And it is only weakly associative. That sounds like
nonsense, but here's what I mean:

\begin{theorem}[Associativity of Multimatrix Multiplication]
\label{mm_associativity}
Let $A$, $B$, and $C$ be multimatricies and $n$ and $m$ in
$\left\{ 0 \right\} \cup \mathbb{Z}^{+}$.
If both operations $(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$
are valid dimensionally, then
\[ (A \mmult{n} B) \mmult{m} C = A \mmult{n} (B \mmult{m} C) \]
\end{theorem}
\begin{proof}
Let $A$, $B$, and $C$ be matricies such that the calculations
$(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$ are both valid.
Then the following vectors must be true by the definiton of multimatrix
multiplication (Thm. \ref{mm_mult}).

\noindent
Since $A \mmult{n} B$ is defined,
\[
  \exists \vec{a}, \vec{n}, \vec{b_1} :
  |\vec{n}| = n \land |A| = \vec{a} \oplus \vec{n} \land |B| = \vec{n} \oplus \vec{b_1} 
\]
Since $B \mmult{m} C$ is defined,
\[
  \exists \vec{b_2}, \vec{m}, \vec{c} :
  |\vec{m}| = m \land |B| = \vec{b_2} \oplus \vec{m} \land |C| = \vec{m} \oplus \vec{c}
\]
Since $(A \mmult{n} B) \mmult{m} C$ is defined, $|\vec{m}| = m$, and $\vec{m}$ is
already established as the left $m$ length portion of $|C|$,
\[ \exists \vec{l} : |A \mmult{n} B| = \vec{l} \oplus \vec{m} \]
Since $A \mmult{n} (B \mmult{m} C)$ is defined, $|\vec{n}| = n$, and $\vec{n}$ is
already established as the right $n$ length portion of $|A|$,
\[ \exists \vec{r} : |B \mmult{m} C| = \vec{n} \oplus \vec{r} \]
We can see that,
\begin{align*}
  |B| &= \vec{n} \oplus \vec{b_1} \\
      &= \vec{b_2} \oplus \vec{m}
\end{align*}
\[ \therefore \vec{n} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{m} \]
So we end up with two cases. Either $\vec{n}$ and $\vec{m}$ overlap in $|B|$, or
they don't.
\begin{case}
$\vec{n}$ and $\vec{m}$ overlap. So we can suppose the existence of
three vectors, $\vec{n_l}$, $\vec{x}$, and $\vec{m_r}$ such that $\vec{x}$
represents the overlapping portion of $\vec{n}$ and $\vec{m}$, so
\[ |B| =  \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ \vec{n} = \vec{n_l} \oplus \vec{x} \]
And,
\[ \vec{m} = \vec{x} \oplus \vec{m_r} \]

Since $|A| = \vec{a} \oplus \vec{n}$ and $|C| = \vec{m} \oplus \vec{c}$,
by the definition of multimatrix multiplication,
\[ |A \mmult{n} B| = \vec{a} \oplus \vec{m_r} \]
And,
\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{c} \]
But because we've presupposed that $(A \mmult{n} B) \mmult{m} C$ is a valid operation,
we know that the rightmost porton of $|A \mmult{n} B|$ must be $\vec{m}$, so
$\vec{a}$ must be divisible into some vector $\vec{a_l}$ and $\vec{x}$ so that
\[ |A \mmult{n} B| = \vec{a_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ \vec{a} = \vec{a_l} \oplus \vec{x} \]
By the same reasoning, since $A \mmult{m} (B \mmult{m} C)$ is a valid operation,
there must exist some $\vec{c_r}$ such that
\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{x} \oplus \vec{c_r} \]
and
\[ \vec{c} = \vec{x} \oplus \vec{c_r} \]

Subsituting in those derived values, we'll see that the expanded version of
our multimatrix shapes become,
\[ |A| = \vec{a_l} \oplus \vec{x} \oplus \vec{n_l} \oplus \vec{x} \]
\[ |B| = \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ |C| = \vec{x} \oplus \vec{m_r} \oplus \vec{x} \oplus \vec{c_r} \]

It's then clear that the shapes of both associations are equal,
\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
Which is a necessary, but not sufficient condition for our proof that
$(A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C)$. We now need to prove
that each of the elements of each resulting multimatrix are the same.

\end{case}

\[
  \vec{b_2} \oplus \vec{c} = \vec{n} \oplus \vec{r}
\]
\[
  \vec{l} \oplus \vec{c} = \vec{a} \oplus \vec{r}
\]
\[
  ((A \mmult{n} B) \mmult{m} C)[\bar{l} \oplus \bar{c}] =
	\sum_{\forall \bar{m}} (A \mmult{n} B)[\bar{l} \oplus \bar{m}]C[\bar{m} \oplus \bar{c}]
\]

\end{proof}

@@

\end{document}

>>>>

\newtheoremstyle{ppart}{}{}{}{}{}{:}{ }{}
\theoremstyle{ppart}
\newtheorem{ppart}{Part}

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

Which isn't a huge improvement over our original notation. What would be great is
if we could define the total derivative without going down into the partial derivatives
at all, which we'll be able to do in later sections. As a sneak peak, that'll look
like this:
\[
\frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} \cos(X)
\]

But that single line will require defining something I'm going to call a cubic
identity, $\Ident^3(|X|)$, as well as multimatrix multiplication.

@@

\begin{definition}[Multimatrix Multiplication]
\label{mm_mult}
Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$,
$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$ with
$n \in \left\{ 0 \right\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size'
of the multiplication operation.
The shape of the result is defined, $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$
and the value of the result is defined,
\[
\forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}):
(A \mmult{n}  B)[\bar{a} \oplus \bar{b}] =
\sum_{\forall \bar{c} \in \Dim(\vec{c})}
  A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
\]
\end{definition}

Like two dimensional matrix multiplication, multimatrix multiplication is
\textit{not} communicative. And it is only weakly associative. That sounds like
nonsense, but here's what I mean.

Multimatrix multiplication may not even make sense dimensionally when you move
around parentheses. Take for example multimatricies $A$, $B$, and $C$ such that,
$|A| = \left<5,3,2\right>$,
$|B| = \left<2,7\right>$, and
$|C| = \left<3,7,2\right>$ where you should be able to see that
$(A \mmult{1} B) \mmult{2} C$ is a valid operation since
$|A \mmult{1} B| = \left<5,3,7\right>$ and
$|(A \mmult{1} B) \mmult{2} C| = \left<5,7\right>$. But
$A \mmult{1} (B \mmult{2} C)$ isn't a valid set of operations since even
$B \mmult{2} C$ is an invalid operation.

But even when the dimensional analysis makes sense, multimatrix multiplication
may not be associative. Take, for example, multimatricies $A$, $B$, and $C$ such
that $|A| = \left<2,2,2,2\right>$, $|B| = \left<2,2,2\right>$, and
$|C| = \left<2,2,2,2\right>$. Let,
\[
 A[\bar{a}] = 
	\left\{
		\begin{array}{ll}
			1 & \mbox{if } \bar{a} = \left<1,1,1,2\right> \\
			0 & \mbox{otherwise}
		\end{array}
	\right.
\]
\[
 B[\bar{b}] = 
	\left\{
		\begin{array}{ll}
			1 & \mbox{if } \bar{b} = \left<1,2,1\right> \\
			0 & \mbox{otherwise}
		\end{array}
	\right.
\]
And
\[
 C[\bar{c}] = 
	\left\{
		\begin{array}{ll}
			1 & \mbox{if } \bar{c} = \left<1,1,1,1\right> \\
			0 & \mbox{otherwise}
		\end{array}
	\right.
\]
Then,
\[
 (A \mmult{2} B)[\bar{x}] = 
	\left\{
		\begin{array}{ll}
			1 & \mbox{if } \bar{x} = \left<1,1,1\right> \\
			0 & \mbox{otherwise}
		\end{array}
	\right.
\]
So,
\[
 ((A \mmult{2} B) \mmult{2} C)[\bar{x}] = 
	\left\{
		\begin{array}{ll}
			1 & \mbox{if } \bar{x} = \left<1,1\right> \\
			0 & \mbox{otherwise}
		\end{array}
	\right.
\]
But, $(B \mmult{2} C)[\bar{x}] = 0$ so $(A \mmult{2} (B \mmult{2} C))[\bar{x}] = 0$
Which goes to show that even though both $(A \mmult{2} B) \mmult{2} C$ and
$A \mmult{2} (B \mmult{2} C)$ are valid calculations which result in multimatrixes
of the same dimensionality, they are not equal so multiplicative associativity
doesn't hold.

However, there are a broad catagory of cases where associativity \textit{does} hold:

\begin{theorem}[Associativity of Multimatrix Multiplication]
\label{mm_associativity}
Let $A$, $B$, and $C$ be multimatricies and $m$ and $n$ in
$\left\{ 0 \right\} \cup \mathbb{Z}^{+}$.
If both operations $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$
are valid dimensionally and $m+n \le ||B||$, then,
\[ (A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C) \]
\end{theorem}
\begin{proof}
Let $A$, $B$, and $C$ be matricies such that the calculations
$(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both valid
and $m + n \le ||B||$.
Then the following must be true by the definiton of multimatrix multiplication
(Def. \ref{mm_mult}).

\noindent
Since $A \mmult{m} B$ is defined,
\[
 \exists \vec{a}, \vec{m}, \vec{b_1} :
 |\vec{m}| = m \land |A| = \vec{a} \oplus \vec{m} \land |B| = \vec{m} \oplus \vec{b_1} 
\]
Since $B \mmult{n} C$ is defined,
\[
 \exists \vec{b_2}, \vec{n}, \vec{c} :
 |\vec{n}| = n \land |B| = \vec{b_2} \oplus \vec{n} \land |C| = \vec{n} \oplus \vec{c}
\]
Since $|B| = \vec{m} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{n}$ and
$||B|| \ge |\vec{m}| + |\vec{n}|$, it must follow that,
\[
 \exists \vec{b} :
 |B| = \vec{m} \oplus \vec{b} \oplus \vec{n}
\]
Even if $\vec{b}$ is an empty vector. Then,
\[ |A \mmult{m} B| = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
\[ |B \mmult{n} C| = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
So,
\[ |(A \mmult{m} B) \mmult{n} C| = |A \mmult{m} (B \mmult{n} C)| \]
Which is necessary, but not sufficient, for our proof.

Looking at each element of the result matricies, let $j$ and $k$ be the values
of some parallel cells in $(A \mmult{m} B) \mmult{n} C$ and
$A \mmult{m} (B \mmult{n} C)$ respectively. Then for some indicies of those cells,
$\bar{a} \oplus \bar{b} \oplus \bar{c} \in
\Dim(\vec{a} \oplus \vec{b} \oplus \vec{c})$,
\begin{align*}
 j
 &= ((A \mmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
 &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
 (A \mmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{n}]
 C[\bar{n} \oplus \bar{c}] \\
 &= \sum_{\forall \bar{n}}
 \left(
  \sum_{\forall \bar{m} \in \Dim(\vec{m})}
	A[\bar{a} \oplus \bar{m}]B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
 \right)
 C[\bar{n} \oplus \bar{c}] \\
 &= \sum_{\forall \bar{n}, \bar{m}}
 A[\bar{a} \oplus \bar{m}]
 B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
 C[\bar{n} \oplus \bar{c}] \\
 &= \sum_{\forall \bar{m}, \bar{n}}
 A[\bar{a} \oplus \bar{m}]
 B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
 C[\bar{n} \oplus \bar{c}] \\
 &= \sum_{\forall \bar{m}}
 A[\bar{a} \oplus \bar{m}]
 \left(
 \sum_{\forall \bar{n}}
  B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
  C[\bar{n} \oplus \bar{c}]
 \right) \\
 &= \sum_{\forall \bar{m}}
 A[\bar{a} \oplus \bar{m}]
 (B \mmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{c}] \\
 &= (A \mmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
 &= k
\end{align*}
Since $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both
the same shape and every cell with the same index in each is equal, the two
values must be equal.
\end{proof}

Multiplicative identities for multimatricies depend on the shape of the
multimatrix they are being multiplied against, just as for regular matricies.
However, the multiplicative identity also greatly depends on the size of
the particular multiplication operation.

\begin{definition}[Multimatrix Identities]
\label{mm_ident}
Let us define $\Ident^n(\vec{v})$ as the $n^{\text{th}}$ order identity with base shape
$\vec{v}$. This $\Ident^n(\vec{v})$ is a multimatrix with shape,
\[ |\Ident^n(\vec{v})| = \bigoplus_{i \in [1, n]} \vec{v} \]
That is, it's shape is $n$ successive concatinations of $\vec{v}$.
Let each element of $\Ident^n(\vec{v})$ is defined as,
\[ \forall \bar{v_1}, \bar{v_2}, \ldots, \bar{v_n} \text{ each in } \Dim(\vec{v}) : \]
\[
 \Ident^n(\vec{v})[\bar{v_1}, \bar{v_2}, \ldots, \bar{v_n}]
 = \left\{
	\begin{array}{ll}
		1 & \mbox{if } \bar{v_1} = \bar{v_2} = \ldots = \bar{v_n} \\
		0 & \mbox{otherwise}
	\end{array}
 \right.
\]

In particular, let us call $\Ident^2(\vec{v})$ the square identity of $\vec{v}$ and
$\Ident^3(\vec{v})$ the cubic identity of $\vec{v}$.
\end{definition}

That definition seems rather arbitrary, but you'll see various orders of identity
pop up in derivatives down the line. For now, let's just look at how the
square identity it relates to a multiplication operation.

\begin{theorem}[Multimatrix Multiplicative Identity]
For all $\vec{m}$ and $\vec{n}$ on which the operations are valid,
\[
 A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A
\]
and
\[
 \Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A
\]
\end{theorem}
\begin{proof}
\begin{ppart}
Let $A$ be a matrix with shape $|A| = \vec{a} \oplus \vec{m}$.
Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
\[ \forall \bar{a} \in \Dim(\vec{a}), \bar{m_1} \in \Dim(\vec{m}) : \]
\[
 (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
 =
 \sum_{\forall \bar{m_2} \in \Dim(\vec{m})}
 A[\bar{a} \oplus \bar{m_2}] \Ident^2(\vec{m})[\bar{m_2} \oplus \bar{m_1}]
\]
Then, by the definition of $\Ident^2(\vec{m})$ (Def. \ref{mm_ident}) it follows
that,
\begin{align*}
 (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
 &=
 \left(
  \sum_{\forall \bar{m_2} \ne \bar{m_1}}
  A[\bar{a} \oplus \bar{m_2}] (0)
 \right)
 +
 \left(
  \sum_{\forall \bar{m_2} = \bar{m_1}}
  A[\bar{a} \oplus \bar{m_2}] (1)
 \right) \\
 \\
 &= 0 + A[\bar{a} \oplus \bar{m_1}] \\
 &= A[\bar{a} \oplus \bar{m_1}]
\end{align*}
Therefore $A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A$
\end{ppart}
\begin{ppart}
Let $A$ be a matrix with shape $|A| = \vec{n} \oplus \vec{a}$.
Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
\[ \forall  \bar{n_1} \in \Dim(\vec{n}), \bar{a} \in \Dim(\vec{a}) : \]
\[
 (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
 =
 \sum_{\forall \bar{n_2} \in \Dim(\vec{n})}
 \Ident^2(\vec{n})[\bar{n_1} \oplus \bar{n_2}]A[\bar{n_2} \oplus \bar{a}] 
\]
Then, by the definition of $\Ident^2(\vec{n})$ (Def. \ref{mm_ident}) it follows
that,
\begin{align*}
 (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
 &=
 \left(
  \sum_{\forall \bar{n_2} \ne \bar{n_1}}
  (0) A[\bar{n_2} \oplus \bar{a}]
 \right)
 +
 \left(
  \sum_{\forall \bar{n_2} = \bar{n_1}}
  (1) A[\bar{n_2} \oplus \bar{a}]
 \right) \\
 \\
 &= 0 + A[\bar{n_1} \oplus \bar{a}] \\
 &= A[\bar{n_1} \oplus \bar{a}]
\end{align*}
Therefore $\Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A$
\end{ppart}
\end{proof}

The square identity also pops up in the derivative of a multimatrix
with respect to itself.

\begin{theorem}[Self Derivative]
Let $X$ be a multimatrix with independent elements. Then,
\[ \frac{dX}{dX} = \Ident^2(|X|) \]
\end{theorem}
\begin{proof}
Let $X$ be a multimatrix of shape $|X|=\vec{x}$ with independent elements.
By the derivative definition (Def. \ref{mm_derivative}),
\[
 \forall \bar{x_1} \in \Dim(\vec{x}),
         \bar{x_2} \in \Dim(\vec{x}):
\]
\[
 \frac{dX}{dX}[\bar{x_1} \oplus \bar{x_2}] = 
 \frac{\partial X[\bar{x_1}]}{\partial X[\bar{x_2}]}
\]
Since each element of $X$ is independent with respect to itself,
\begin{align*}
 \frac{dX}{dX}[\bar{x_1} \oplus \bar{x_2}]
 &= \left\{
	\begin{array}{ll}
		1 & \mbox{if } \bar{x_1} = \bar{x_2} \\
		0 & \mbox{otherwise}
	\end{array}
 \right. \\
 &= \Ident^2(\vec{x})[\bar{x_1} \oplus \bar{x_2}]
\end{align*}
Therefore $dX/dX = \Ident^2(|X|)$
\end{proof}

The cubic identity, strangely enough, pops up in the derivative of elementwise
functions.

\begin{theorem}[Elementwise Derivative]
Let $M$ be an element wise function on $X$. That is, Let $M(X)$ be a function
such that,
\[ M(X) : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\vec{x}} \]
And which applies the same scalar function to each element of $X$, 
\[ M(X)[\bar{x}] = m(X[\bar{x}]) \]
Also, let $M'$ be the elementwise function on $X$ which applies the derivative
of $M$'s associated scalar function to each element of $X$. That is,
\[ M'(X)[\bar{x}] = m'(X[\bar{x}]) \]
Then,
\[ \frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} M'(X) \]
\end{theorem}
\begin{proof}
By the definition of a multimatrix derivative,
\[ \forall \bar{m} \in \Dim(|M|), \bar{x} \in \Dim(|X|) : \]
\begin{align*}
 \frac{dM}{dX}[\bar{m} \oplus \bar{x}]
 &= \frac{\partial M[\bar{m}]}{\partial X[\bar{x}]} \\
 &= \frac{\partial m(X[\bar{m}])}{\partial X[\bar{x}]} \\
 &= \left\{
	\begin{array}{ll}
		m'(X[\bar{m}]) & \mbox{if } \bar{m} = \bar{x} \\
		0 & \mbox{otherwise}
	\end{array}
 \right. \\
 &= \delta_{\bar{m} \bar{x}} m'(X[\bar{m}])
\end{align*}
Since, by our definition of elementwise function, $|M| = |X|$, we can
say that, 
\begin{align*}
 (\Ident^3(|X|) \mmult{||X||} M'(X))[\bar{m} \oplus \bar{x}]
 &= \sum_{\forall \bar{y} \in \Dim(|X|)}
 \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] M'(X)[\bar{y}] \\
 &= \sum_{\forall \bar{y} \in \Dim(|X|)}
 \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
 &= \sum_{\forall \bar{y} = \bar{m} = \bar{x}}
 \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
 &= \left\{
	\begin{array}{ll}
		m'(X[\bar{m}]) & \mbox{if } \bar{m} = \bar{x} \\
		0 & \mbox{otherwise}
	\end{array}
 \right. \\
 &= \delta_{\bar{m} \bar{x}} m'(X[\bar{m}])
\end{align*}
Therefore $dM/dX = \Ident^3(|X|) \mmult{||X||} M'(X)$
\end{proof}

\begin{theorem}[Identity Contraction]
For all $m, n, k \in \mathbb{Z}^+$ and $\vec{x}$ as a valid multimatrix shape,
where $m > k$ and $n > k$,
\[ \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Communicative Identity Multiplication]
\[ \Ident^n(\vec{x}) \mmult{k|\vec{x}|} A = A \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\section{Other Operations With Multimatricies}
Other operations include...

\begin{definition}[Multimatrix Scalar Multiplication]
\[ sA = ...\]
\end{definition}

\subsection{Addition}

\begin{definition}[Multimatrix Addition]
Bla
\[ A + B = C \]
\end{definition}

\begin{theorem}[Communicative Property of Multimatrix Addition]
Bla
\[ A + B = B + A \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Associative Property of Multimatrix Addition]
\[ (A + B) + C = A + (B + C) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Multimatrix on Multimatrix Distributive Property]
\[ A \mmult{n} (B + C) = A \mmult{n} B + A \mmult{n} C \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Scalar on Multimatrix Distributive Property]
\[ s(A + B) = sA + sB \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

@@

\section{Integration}

I think, I'm not sure, but I think that the integral of a multimatrix function should
be defined,

\[
 \int_A^B F(X) dX = \lim_{n \to \infty}
 \sum_{i=1}^n
  F\left(A+\frac{i}{n}(B-A)\right)
  \mmult{||X||}
  \left(\frac{B-A}{n}\right)
\]

Which, I have very little idea what that means geometriclly, but
if you let $G(X) = \int_A^X F(Y) dY$ you seem to end up with $dG/dX = F(X)$.

Maybe... well look at it this way. $F(X)$ is a function which produces some,
afine-like transformation multimatrix for multimatricies of shape $|X|$,
since it must have a right hand shape of $\ldots \oplus |X|$. This integration
occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
transformation and adding up the results of the transformed multimatricies with
a weight proportional to the step size.

So, it's sort of like a line integral but not really. They're related somehow.
\end{document}
